\documentclass[10pt]{resume}

\usepackage{array}
\usepackage[margin=0.65in]{geometry}
\usepackage[scaled]{helvet}

\geometry{top=10mm}

\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\pagenumbering{gobble}

\name{Matthew Stanley}
\vspace{0.5em}
\contact{34 Cardinal Way}{Middlebury}{VT 05753}
{stanley.t.matthew@gmail.com}{(802) 989-2201}{http://mtstanley.tech}

\section{Education}

\locationsubsection{Middlebury College}{Middlebury, VT}
\textbf{Major:} Bachelor of Arts in Computer Science, \textit{summa cum laude} \hfill February 2012--February 2016\\
\textbf{Minor:} Mathematics\\
\textbf{GPA:} \textit{Major:} 3.93 \textit{Overall:} 3.91\\
\textbf{Honors:} Phi Beta Kappa, College Scholar 6 semesters

\section{Technical Skills}
\begin{tabular}{>{\bfseries}l l}
Programming Languages:  &  Python, Java, C, Bash, JavaScript, HTML, CSS \\
Libraries \& Frameworks:&  Backbone.js, Node.js, WebGL, Flask, jQuery   \\
Operating Systems:      &  Unix, Mac OS X, Linux (Arch, Fedora)         \\
Dev Tools:              &  git, gcc, make                               \\
\end{tabular}

\section{Experience}

\locationsubsection{Middlebury College}{Middlebury, VT}
\expblock
{Research Assistant (Computer Vision) \textnormal{Department of Computer Science}}{Summer 2015} 
{ 
    \item Designed and developed two graphical applications to compute and
    visualize a selection of matching costs for stereo image pairs. These
    applications also allow the user to manipulate the images including:
    omnidirectional movement and horizontal/vertical image warping around
    an anchor point.

    \item Implemented both a native and a web-based application, in C++ and
    JavaScript, respectively.

    \item Using the WebGL API and GLSL, parallelized the compute-intensive
    image processing to take advantage of GPGPU allowing for interactive
    speeds within a web browser environment.
}

\expblock {Teaching Assistant \textnormal{Department of Computer
Science}}{September 2014--December 2015} 
{
    
    \item Computing for the Sciences (Fall 2015): Graded Python
    programming assignments for a class of 60 students, provided one-on-one
    mentoring in a lab class of 30 students.

    \item Data Structures (Spring 2015): Provided both numerical and
    written feedback on Java programming assignments for a class of 60
    students.

    \item Computing for the Sciences (Fall 2014): Graded a class of 30
    students on both style and correctness of programming assignment solutions
    written in Python. 
}

\expblock
{Research Assistant \textnormal{Department of Chemistry}}{Summer 2012}
{
    \item Synthesized the protein methionine aminopeptidase (METAP 2) used for
    researching the enzyme's role in angiogenesis.

    \item Used UV-Vis spectroscopy to test the quality and quantity of protein
    produced. 
    

    \item Created and presented a poster for the Middlebury College research
    symposium. 
}

\locationsubsection{American Flatbread}{Middlebury, VT}
\expblock
{Assistant Kitchen Manager}{June 2010--present}
{
    \item Trained on all positions in the restaurant, both front and back of
    house. Proficient enough to smoothly manage 400 cover nights. Create
    and execute catering menus for parties exceeding 100 individuals.
        
    \item Design and oversee the creation of new menu items and weekly
    specials alongside the head chef.

    \item Manage the kitchen staff in the absence of the head chef.
}

\end{document}
